Inferring Graphics Programs from Images

### 2017-05-17 paper.tex
abstract

\begin{abstract}
\end{abstract}

@@

  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer: \LaTeX};

@@

%  \node at (canvas.x,canvas.y) {Canvas};
\end{tikzpicture}
\caption{Our neural architecture for inferring the execution trace of a graphics program from its output. \textcolor{blue}{Blue}: network inputs. Black: network operations. \textcolor{red}{Red}: samples from a multinomial. \texttt{Typewriter font}: network outputs. Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me).}}  \label{architecture}
\end{figure}
\begin{table}
\begin{tabular}{ll}\toprule
  \begin{tabular}{l}
    \verb|circle|$(x,y)$
  \end{tabular}& \begin{tabular}{l}
    Circle at $(x,y)$
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|rectangle|$(x_1,y_1,x_2,y_2)$
  \end{tabular}&\begin{tabular}{l}
    Rectangle with corners at $(x_1,y_1)$ \& $(x_2,y_2)$
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|LINE|$(x_1,y_1,x_2,y_2,$\\
    \hspace{1cm}$\text{arrow}\in\{0,1\},\text{dashed}\in\{0,1\})$
  \end{tabular}&\begin{tabular}{l}
    Line from $(x_1,y_1)$ to  $(x_2,y_2)$,\\\hspace{1cm}optionally with an arrow and/or dashed
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|STOP|
  \end{tabular}&\begin{tabular}{l}
    Finishes execution trace inference
    \end{tabular}
\\  \bottomrule
\end{tabular}
\caption{The deep network in (\ref{architecture}) predicts drawing commands, shown above.}
\label{drawingCommandTable}
\end{table}

@@

\begin{figure}\centering
  \begin{minipage}{0.35\textwidth}
    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-58-7.png}}\end{minipage}
    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
    \caption{Network is trained to infer execution traces for randomly generated figures like the two shown above.}\label{trainingData}
  \end{minipage}\hfill
  \begin{minipage}{0.6\textwidth}
    \includegraphics[width = 4cm]{figures/editDistance.png}
    \includegraphics[width = 4cm]{figures/accuracy.png}
      \caption{Using the model to parse latex output. The model is trained on diagrams with up to 8 objects. As shown above it generalizes to scenes with many more objects. Neither the stochastic search nor the neural network are sufficient on their own.}\label{syntheticResults}
    \end{minipage}

@@

\begin{table}[H]
  \begin{tabular}{rl}
  Program$\to$&Command; $\cdots$; Command\\
  Command$\to$&\texttt{circle}(Expression,Expression)\\
  Command$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
  Command$\to$&\texttt{LINE}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
  Command$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ }Program\texttt{ \}}\\
  Command$\to$&\texttt{REFLECT}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
  Expression$\to$&\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}\\
  Var$\to$&A free (unused) variable\\
  \mathcal{Z}$\to$&an integer\\
  Axis$\to$&\texttt{X = }\mathcal{Z}\\
  Axis$\to$&\texttt{Y = }\mathcal{Z}
  \end{tabular}
  \caption{Grammar over graphics programs. We allow loops (\texttt{for}), vertical/horizontal reflections (\texttt{REFLECT}), and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}\label{DSL}
\end{table}

Given the DSL and a trace $T$, we want to recover a program that both evaluates to $T$
and, at the same time, is the ``best'' explanation of $T$.
For example, we might prefer more general programs or, in the spirit of Occam's razor,
prefer shorter programs.
We wrap these intuitions up into a cost function over programs,
and seek the minimum cost program consistent with $T$:
\begin{equation}
  \text{program}(T) = \argmin_{\substack{p\in \text{DSL}\\p \text{ evaluates to } T}} \text{cost}(p)\label{programObjective}
\end{equation}
We define the
cost of a program to be the number of statements it contains, where a
statement is a ``Command'' in Table~\ref{DSL}.
%\remark{The flow here is a bit off/backwards. ``We want a program that evaluates to $T$ and also minimizes some measure of program cost''---why do we care about cost? It'd be better to start by making a ``Bayesian Occam's razor'' appeal (e.g. the most compact/general program is the more likely explanation) and then saying that one way to do this is to minimize a cost function which is proportional to program length.}

@@

  \pagebreak
  \section{Preliminary extrapolation results}

\pagebreak
  \section{Preliminary Synthesis results} 
%\input{synthesizerOutputs.tex}

>>>>

\begin{abstract}
  We introduce a model that learns to convert simple hand drawings
  into graphics programs written in a subset of \LaTeX.~The model
  combines techniques from deep learning and program synthesis.  We
  learn a neural network that proposes plausible drawing primitives
  that explain an image.  From these deep net proposals we can use
  program synthesis techniques to recover a graphics
  program with constructs like variable bindings, iterative loops, or
  simple kinds of conditionals. With a graphics program in hand,
  we can extrapolate figures, form visual analogies, \remark{what else should go here?}, and correct errors made by the deep network.
  Taken together these results are a step towards
  agents that induce programs from perceptual input.  
\end{abstract}

@@

  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer: \LaTeX~Ti\emph{k}Z};

@@

%  \node at (canvas.x,canvas.y) {Canvas};
\end{tikzpicture}
\caption{Our neural architecture for inferring the execution trace of a graphics program from its output. \textcolor{blue}{Blue}: network inputs. Black: network operations. \textcolor{red}{Red}: samples from a multinomial. \texttt{Typewriter font}: network outputs. Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me).}}  \label{architecture}
\end{figure}
\begin{table}
\begin{tabular}{ll}\toprule
  \begin{tabular}{l}
    \verb|circle|$(x,y)$
  \end{tabular}& \begin{tabular}{l}
    Circle at $(x,y)$
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|rectangle|$(x_1,y_1,x_2,y_2)$
  \end{tabular}&\begin{tabular}{l}
    Rectangle with corners at $(x_1,y_1)$ \& $(x_2,y_2)$
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|line|$(x_1,y_1,x_2,y_2,$\\
    \hspace{1cm}$\text{arrow}\in\{0,1\},\text{dashed}\in\{0,1\})$
  \end{tabular}&\begin{tabular}{l}
    Line from $(x_1,y_1)$ to  $(x_2,y_2)$,\\\hspace{1cm}optionally with an arrow and/or dashed
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|STOP|
  \end{tabular}&\begin{tabular}{l}
    Finishes execution trace inference
    \end{tabular}
\\  \bottomrule
\end{tabular}
\caption{The deep network in (\ref{architecture}) predicts drawing commands, shown above.}
\label{drawingCommandTable}
\end{table}

@@

\begin{figure}\centering
  \begin{minipage}{0.35\textwidth}
    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-58-7.png}}\end{minipage}
    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
    \caption{Network is trained to infer execution traces for randomly generated figures like the two shown above.}\label{trainingData}
  \end{minipage}\hfill
  \begin{minipage}{0.6\textwidth}
    \includegraphics[width = 4cm]{figures/editDistance.png}
    \includegraphics[width = 4cm]{figures/accuracy.png}
      \caption{Using the model to parse latex output. The model is trained on diagrams with up to 8 objects. As shown above it generalizes to scenes with many more objects. Neither the stochastic search nor the neural network are sufficient on their own. \# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}
    \end{minipage}

@@

\begin{table}[H]
  \begin{tabular}{rl}\toprule
  Program$\to$&Command; $\cdots$; Command\\
  Command$\to$&\texttt{circle}(Expression,Expression)\\
  Command$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
  Command$\to$&\texttt{line}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
  Command$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ if }$(\text{Var} > 0)$\texttt{ \{ }Program\texttt{ \}; }Program\texttt{ \}}\\
  Command$\to$&\texttt{reflect}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
  Expression$\to$&\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}\\
  Var$\to$&A free (unused) variable\\
  \mathcal{Z}$\to$&an integer\\
  Axis$\to$&\texttt{X = }\mathcal{Z}\\
  Axis$\to$&\texttt{Y = }\mathcal{Z}\\\bottomrule
  \end{tabular}
  \caption{Grammar over graphics programs. We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertical/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}\label{DSL}
\end{table}

Given the DSL and a trace $T$, we want to recover a program that both evaluates to $T$
and, at the same time, is the ``best'' explanation of $T$.
For example, we might prefer more general programs or, in the spirit of Occam's razor,
prefer shorter programs.
We wrap these intuitions up into a cost function over programs,
and seek the minimum cost program consistent with $T$:
\begin{equation}
  \text{program}(T) = \argmin_{\substack{p\in \text{DSL}\\p \text{ evaluates to } T}} \text{cost}(p)\label{programObjective}
\end{equation}
We define the
cost of a program to be the number of statements it contains, where a
statement is a ``Command'' in Table~\ref{DSL}.
We also penalize using more distant constants,
which encourages reuse of coefficients.
%\remark{The flow here is a bit off/backwards. ``We want a program that evaluates to $T$ and also minimizes some measure of program cost''---why do we care about cost? It'd be better to start by making a ``Bayesian Occam's razor'' appeal (e.g. the most compact/general program is the more likely explanation) and then saying that one way to do this is to minimize a cost function which is proportional to program length.}

@@

%\input{synthesizerOutputs.tex}
